---
title: "Example Usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
Below is a basic example of how to use each of the four functions included in this package.

# Install pacakge
```{r setup}
# Download the package
devtools::install_github("UBC-MDS/nameformeR")
```
# Functions

## 1. find_name()

A function to generate a random set of 10 suggested baby names based on the given limitations.
- if the given limitation can match to at least 10 names, a list of 10 names will be provided

```{r find_name_a}
find_a <-  find_name("F", "A", length=3)
find_a
```

- if the given limitation can only match less than 10 names, all matched names will be provided

```{r find_name_b}
find_b <-  find_name("m", "b", length=9)
find_b
```

## 2. find_old_name()

A function to generate a random set of suggested neutral(by default) baby names based on the given time period and sex.

```{r find_old_name}
old_name <-  find_old_name('1980s', limit=3)
old_name
```

## 3. find_similar_name()

A function to generate a random list of names that sound similar to a given user input name.

```{r find_similar_name}
similar_name <-  find_similar_name('Daniel', limit=5)
similar_name
```

## 4. find_unisex_name()

```{r find_unisex_name}
unisex_name <-  find_unisex_name(bar=0.02, limit=7)
unisex_name
```




